Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Fixed sphlib reference to bmw, added sphlib description and removed supercop time column

>>>>

\paragraph{Sphlib} is a C and Java library made by Thomas Pornin
\footnote{\url{http://www.saphir2.com/sphlib/}}, which contains all the second
round \ac{SHA}-3 candidates. Some of the same implementations are also found in
\ac{SUPERCOP}, while others, like the Cubehash implementation we have used is
not.
